% resume.tex
% sample template copied from https://web.archive.org/web/20150807054721/http://www.toofishes.net/media/extra/sample-resume.pdf

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in,bmargin=0em]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}

\usepackage{libertine}
\usepackage{libertinust1math}
\usepackage[T1]{fontenc}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

\definecolor{customUrlColor}{HTML}{0c0d4c}
\hypersetup{colorlinks=true, allcolors=customUrlColor}

\begin{document}

\begin{center}
    % \vspace*{-2.5em}
    {\LARGE \textbf{Isaac K. Boaz}}

    \ \ Seattle, WA\ \ \textbullet
    \ \ (208) 473-6497\ \ \textbullet
    \ \ isaac.k.boaz@gmail.com
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
    \parskip=0.1em

    \item
          \headerrow
          {\textbf{Trimble}}
          {\textbf{Seattle, WA}}
          \\
          \headerrow
          {\emph{Software Engineering Intern}}
          {\emph{06/2024 -- 09/2024}}
          \begin{itemize*}
              \item Contributed to the development of a \href{https://github.com/trimble-oss/tierceron/}{Golang-based secrets manager}.
              \item Resolved a 4-year-old bug in a JSX-based web application within 4 days.
              \item Identified, prepared, and deployed Windows agents for the secrets manager.
              \item Created shell and Azure DevOps scripts to automate releases and workflows.
              \item Met with a Scrum team weekly to understand responsibilities and blocks.
          \end{itemize*}

    \item
          \headerrow
          {\textbf{Western Washington University}}
          {\textbf{Bellingham, WA}}
          \\
          \headerrow
          {\emph{Computer Science Teacher Assistant}}
          {\emph{01/2024 -- 06/2024}}
          \begin{itemize*}
              \item Held office hours to assist students with assignments and projects.
              \item Provided feedback and grades on assignments, projects, and quizzes.
              \item Worked with professors to ensure students completed assignments and understood course material.
          \end{itemize*}

    % \item
    %       \headerrow
    %       {\textbf{Nordstrom}}
    %       {\textbf{Seattle, WA}}
    %       \\
    %       \headerrow
    %       {\emph{Logistics Processor}}
    %       {\emph{06/2023 -- 09/2023}}
    %       \begin{itemize*}
    %           \item Gained quick familiarity of store layout to efficiently gather merchandise.
    %           \item Coordinated with teammates to reach goals, delegate tasks, and meet quotas.
    %           \item Processed 15+ customer orders per day, ensuring accuracy and quality of order packing.
    %       \end{itemize*}
\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
    \parskip=0.1em

    \item
          \headerrow
          {\textbf{Western Washington University}}
          {\textbf{Bellingham, WA}}
          \\
          \headerrow
          {\emph{College of Science and Engineering, B.S. Computer Science}}
          {\emph{2022 -- 2024}}
          \begin{itemize*}
              \item Minor in Mathematics.
              \item Graduated December 2024.
                    %   \item Expanded work stack to include \LaTeX, GitHub Codespaces, and Remote SSH Development.
          \end{itemize*}
    \item
          \headerrow
          {\textbf{South Seattle College}}
          {\textbf{Seattle, WA}}
          \\
          \headerrow
          {\emph{College of Science and Engineering, A.S. Computer Science}}
          {\emph{2021 - 2022}}
          %   \begin{itemize*}
          %       \item Graduated 2022 with a 3.36 GPA.
          %   \end{itemize*}
\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Projects}

\begin{itemize}
    \parskip=0.1em
    \item
          \headerrow
          {\textbf{EdgeGamers Organization}}
          {\href{https://edgegamers.com}{https://edgegamers.com}}
          \\
          \headerrow
          {\emph{Software Engineer, Volunteer}}
          {\emph{2022 -- Present}}
          \begin{itemize*}
              \item Developed projects including Java \& C\# server plugins and maintenance.
              \item Managed and maintained multiple videogame servers, set up and separated production / development
                    servers using automated systems including Docker, GitLab, and GitHub.
              \item Coordinated with a team of 26 people via GitLab to ensure tasks, goals, and issues were completed promptly.
              \item Managed public-facing issue trackers, working with divisional managers to assure issues
                    were marked, responded to, and resolved as appropriate.
              \item Documented new policies, procedures, and systems to allow for easier onboarding and training of new members.
          \end{itemize*}
    \item
          \headerrow{\textbf{Jailbreak}}{\href{https://github.com/edgegamers/Jailbreak}{https://github.com/edgegamers/Jailbreak}}
          \begin{itemize*}
              \item A Counter-Strike 2 server plugin written in C\# to allow for the Jailbreak gamemode to be easily played.
              \item Integrated with a C++ based MetaMod plugin using the CounterStrike Sharp framework.
              \item Utilizes MySQL for player state and stats management.
          \end{itemize*}
    \item
          \headerrow
          {\textbf{AdminMode}}
          {\href{https://git.msws.xyz/MS/admin-mode}{https://git.msws.xyz/MS/admin-mode}}
          \begin{itemize*}
              \item A Minecraft plugin written in Java that allows server moderators / administrators to easily enter \emph{admin mode}.
              \item Entering / leaving \emph{admin mode} preserves player state to reduce interruptions.
              \item Integrates with DiscordSRV for transparent logging to upper management.
          \end{itemize*}
\end{itemize}

\hrule
\vspace{-0.4em}

\subsection*{Miscellaneous}

\begin{indentsection}{\parindent}
    \hyphenpenalty=1000
    \begin{description*}
        \item[Skills:]
              C\#, Golang, Java, JavaScript / TypeScript, SQL, \LaTeX, Git, Docker, DevOps, AWS, Google
        \item[GitHub:] \href{https://github.com/MSWS}{https://github.com/MSWS}
        \item[Website:] \href{https://msws.xyz}{https://msws.xyz}
    \end{description*}
\end{indentsection}

\end{document}
