% resume.tex
% sample template copied from https://web.archive.org/web/20150807054721/http://www.toofishes.net/media/extra/sample-resume.pdf

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,tmargin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}

\usepackage{libertine}
\usepackage{libertinust1math}
\usepackage[T1]{fontenc}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

\definecolor{customUrlColor}{HTML}{0c0d4c}
\hypersetup{colorlinks=true, allcolors=customUrlColor}

\begin{document}

\begin{center}
    % \vspace*{-3.5em}
    {\LARGE \textbf{Isaac K. Boaz}}

    \ \ Seattle, WA\ \ \textbullet
    \ \ (208) 473-6497\ \ \textbullet
    \ \ isaac.k.boaz@gmail.com
\end{center}

\hrule
\vspace{0.4em}

\parskip=0.1em

\noindent
To whom it may concern, \\
\indent
I am on course to graduate from Western Washington University at the end of
December, and am beginning the search for a fun, enjoyable, and challenging job
in the Software Engineering field. During my internship at Trimble (a large
company), I came to the realization that I have a preference towards more
on-hands, concrete work; in my mind, Valve has shown itself to be a pioneer for
developers and engineers in its industry while achieving this goal.

With my years of experience working for a gaming community where I developed new
servers, plugins, and tools (including CS:GO, Counter-Strike 2, and
Team Fortress 2), I have been able to develop a strong grasp of the technologies
that Valve uses. The projects that Valve has worked on have been revolutionary
in nearly every regard, and I would love to work on projects that are as
innovative and groundbreaking as those that Valve has worked on.

Though I may not have as much experience as others, I take great
pride in my work, my attention to detail, and the quality of my projects. I
am always excited to take on new challenges (games, languages, infrastructure,
writing, etc.), and I am confident that I would be a great fit for the team at
Valve. \\

Thank you for your time and consideration. I look forward to hearing from you.

Sincerely, \\
\indent\indent
Isaac K. Boaz
\end{document}
